Ground state energy of quantum dots using the coupled cluster method

### 2018-04-10 project_2/article/article.tex
Add TODO
Add start of the coupled cluster section

\section{Introduction}
    In this project we will study the ground state energy of quantum dots.

@@

>>>>

\section{Introduction}
    %TODO: Add explanation on why the many-body problem becomes intractable.
    % This can be shown by demonstrating that the true wavefunction of the system
    % must be a linear combination of all possible Slater detemerminants built up
    % from permutations of the single particle functions in the basis. Thus the
    % energy equation becomes too large.
    In this project we will study the ground state energy of quantum dots.

@@

    \subsection{The coupled cluster approximation}
        We approximate the true wavefunction, $\ket{\Psi}$, of the system by the
        coupled cluster wavefunction, $\ket{\Psi_{\text{CC}}}$, defined as
        \begin{align}
            \ket{\Psi_{\text{CC}}}
            &\equiv e^{T}\ket{\Phi_0}.
        \end{align}
